This is the Title

### 2017-03-12 trunk/abc/paper/paper.tex
Almost filled postreloc. Lunch time

% Literate executable, knuth
% In the dead space of the binary, put this paper or part of it

@@

TODO: Convert byte table thing into ascii. Unfortunately can't fit
the whole 256x256 thing, so maybe 128x128 with a small amount of
cropping, then a 1:1 zoom on the sierpinski triangle part?

this page confirms the wrap-around with jumps btw:
http://www.felixcloutier.com/x86/Jcc.html
(Probably already in the x86 manual actually?)

@@

BTW here is eicar:

X5O!P%@AP[4\PZX54(P^)7CC)7}$EICAR-STANDARD-ANTIVIRUS-TEST-FILE!$H+H*

It does indeed use self-modifying code to create the interrupt
instructions, which it uses to print the string and exit.

@@

write about load16 tmp <- tmp; it's amazing now.
(benchmark history shows performance gains..)

@@

``interrupt is a way of telling the operating system: Check this out!''

@@

>>>>

% Literate executable, knuth

@@

@@

@@

@@

@@

awesome text art headings?

Truly self-documenting
Giving new meaning to "program committee" "evaluating" my paper
For good reasons that I will explain later...

I was kidding when I said the x86 architecture is elegant.

Dr. Dobbs Journal typing in the program

ES segment must be used for IN?

TODO: X86 vs x86

(Idea: ladder is actually interspersed in code, by putting some long instruction
byte (that takes several arguments) before DEC SP JNZ +7e? We can jump directly
to the jump, but if executed in a normal synchronized flow, then it executes some
instruction that does nothing (load immediate?).)

(Idea: Once we've gone past EIP=0xFFFF, we can still execute code from our binary.
It may be possible to get back to CS by doing a jump with the address/operand size prefix?
Neither one has an effect in DOSBox, which may be a bug? Anyway, if an interrupt
is triggered while we're up here, it seems like it only does a 16-bit RET, so that's
kinda busted.)

missing condition; ``left-facing''

RISC ROLL

video: bingo of tom 7 video themes (``retro'', ``alphabet,''
``fractal geometry'')
